---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vembedr); library(htmltools); library(leaflet)
```

<link rel="stylesheet" href="styles.css" type="text/css">

<style type="text/css">
body{ /* Normal  */ font-size: 16px; font-family: Arial; color:black}
td {  /* Table  */ font-size: 8px;}
h1.title {font-size: 38px; color: DarkRed;}
h1 { /* Header 1 */ font-size: 28px; color: Black;}
h2 { /* Header 2 */ font-size: 22px; color: Black;}
h3 { /* Header 3 */ font-size: 18px; color: Black;}
code.r{ /* Code block */ font-size: 12px;}
pre { /* Code block - determines code spacing between lines */ font-size: 14px;}
</style>

# Fieldwork

Here are sites where my colleagues and I have developed field research projects. The map is still under-construction; check back in the future for project descriptions and pictures.

```{r leaflet, echo=FALSE}

Name = c("Conecuh National Forest, Alabama","Yunnan Province, China","Lower Canyons of the Rio Grande","Blue Ridge Mountains","Spring Creek, Georgia","La Selva Biological Station, Costa Rica","Conger Mountain, Utah", "Choctawhatchee River, Florida", "Auburn University Museum of Natural History")

Topic = c("Field studies of Gopher Tortoise survival and population genetic structure; reintroduction of an endangered snake","Biodiversity surveys of reptiles and bats in karst caves","Formative wilderness adventure","Phylogenetic studies of salamanders","Demographic studies of Alligator Snapping Turtles","Field studies and experimental manipulations of frog and lizard population regulation","Feral horse demographic research","Studies of hybridizing freshwater turtles","Taxonomic and phylogenetic studies of amphibians and reptiles")

coords <- read.csv(textConnection(
"Lat,Long, 
31.126,-86.753, 
22.000, 100.8000,
29.633241, -102.74,
34.799517, -84.576,
30.937477, -84.7426,
10.425307, -84.017,
39.232, -113.699,
30.9869, -85.829722,
32.599068, -85.482878"
))

df = cbind(Name,Topic,coords)

labs <- lapply(seq(nrow(df)), function(i) {
  paste0( '<p>', df[i, "Name"], '<p></p>', 
          df[i, "Topic"]) 
})

leaflet(df) %>% addTiles() %>%
  addMarkers(~Long, ~Lat, label = lapply(labs, htmltools::HTML)) %>%
  addProviderTiles(providers$OpenMapSurfer.Roads)
```

Here are videos from some favorite field excursions - for research or just for fun.  

```{r library(vembedr), echo=FALSE}
embed_vimeo("152795925")

embed_vimeo("291925447")

embed_vimeo("491806654")

embed_vimeo("574933065")
```
